A practical guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light conditions

### 2016-07-30 Main.Rmd
ECBにはsupplementalがないらしいので、構成を結構変更。 RM指摘に対応した削りが進み、2867 words

---
title: "A practical guide for selecting the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate"
author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
bibliography: ~/GitHub/BeeLabR/BibTex/with.bib
csl: ECB.csl
output:
  html_document:
    toc: TRUE
    depth: 3
    theme: sandstone
    self_contained: TRUE
    fig_caption: TRUE
    pandoc_args: [
    "--latexmathml"
    ]
  # word_document:
  #   pandoc_args: [
  #   "--latexmathml"
  #   ]
---

```{r load, echo = F, message = F}
evalFig <- T

if(evalFig){
devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup_silent.R")
} else {
library(knitr)
}

opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 5,
               out.width = '500pixel', out.height = '500pixel', dpi = 100,
               message = FALSE, warning = FALSE, cache = F, eval = T)
```

```{r Captions}
CapETRs <-
  "Fig. 1  The conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR). Electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured using PSII-light (A, C) and PSI-light (B, D) were shown."

CapInteract <-
  "Fig. 2  The conceptual diagram of the photosynthetic electron transport rates per absorbed photons by the photosystems grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."
```

@@

@@

@@

  The photosynthetic rate is one of the most important and fundamental traits of the plant.
  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions.
  The measured rates are also used for the calculation of the other photosynthetic parameters, such as light, water, and nitrogen use efficiencies.
  In agricultural and horticultural studies, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rate and calculated parameters. 
  Therefore, the accurate measurements of the photosynthetic rate must be essential.

  A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for the measurement (i.e. measuring light or actinic light) affected the net photosynthetic rates (*P*~n~) of leaves [e.g. @McCree1972AM; @Inada1976PCP].
  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a single-level SPD of measuring light irrespective of the leaf growth conditions in these fields.
  The most widely-used measuring light might be mixture of blue + red LED light (BR-light) provided by light sources installed in commercial photosynthesis analyzing systems.
  The use of the artificial light sources might enable precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf thereby ensure the reproducibility and reliability of the experiments.

  @Walters2005JXB pointed out that the measurements with a SPD of light different from growth light do not necessarily reflect the functioning of the photosynthesis under growth conditions.
  Our recent study, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently the *P*~n~ of the leaves were compared under BR-light and light with the SPD resembling that of sunlight.
  The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable under artificial sunlight [@Murakami_et_al2016PP].
  Based on the results obtained from the measurement under BR-light, the prospective growth rate of WFR-plants may be evaluated to be smaller than that of W-plants despite the comparable rates under the sunlight.

  The effect of the SPD of growth light on the *P*~n~ depended on the level of the SPD of measuring light.
  In other words, the SPDs of growth light and measuring light interacted on the *P*~n~ of a leaf.
  In this short article, we introduce a plausible cause of the interaction and several articles reporting the interaction.
  We then suggest the situations where the interaction should be cared.
  We also discuss the good practice for the selection of the SPD of measuring light used for *P*~n~ measurements.
  The SPD of light affects the photosynthesis through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], the photoinhibition [@Zavafer_et_al2015JPP], and the light-penetrating depth within a leaf [@Terashima_et_al2009PCP].
  Although these subjects are not referred in this article, the cited review articles on these topics are available.

# How the interaction is generated?

  Fundamental knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
  Light energy absorbed by a leaf drives the electron transport and thereby the photosynthetic O~2~ evolution and CO~2~ uptake.
  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
  The reactions are powered by excitation energy derived from absorbed photons.
  The excitation energy transferred to the reaction centers of the photosystems is consumed by the photochemical reactions in units of moles.
  The serial photochemical reactions at PSII and PSI enables electron transfer against the redox potential (called the Z scheme).
  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membranes should be limited by the slowest step (Fig. 1).
  When PSII absorbs excess excitation energy under PSII-biased light, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII should be lowered (Fig. 1C).
  When PSI absorbs excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 1B).
  In both cases, the excess energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
  An imbalance excitation between the photosystems can harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
  Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.

  <!-- **おまけ部分** -->
  <!-- Note that the balanced distribution might not be a fifty-fifty. -->
  <!-- Even in a dark adapted helthy leaf, the yield of PSII cannot exceed 0.84 (i.e. Chl fluorescence parameter *F*~v~/*F*~m~). -->
  <!-- Although there is no clear consensus, the maximum yield of PSI seems to be greater than that of PSII. -->
  <!-- Therefore, under the fifty-fifty distribution, the energy supply to PSII is insufficient and that to PSI is excessive. -->
  <!-- A little bit greater distribution to PSII might be required to make maximum use of the absorbed photons. -->
  <!-- Gentyに触れるか？AEF -->

  <!-- The imbalance in the EED between the photosystems is supposed to occur ordinarily (どこで？太陽光？). -->
  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  Such an imbalanced excitation is caused by the facts that only chl *a* can absorb the longer wavelengths of light and that PSI contains a greater amount of chl *a* than PSII.
  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependencies of the EED is a determinant of the EED under a given SPD of light.
  In several studies of the SPD acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI
  This categorization is defined in the relative scale, not in the absolute scale.
  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 1A), can overexcite PSII in PSI-light-grown leaves (Fig. 1C).
  Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.

  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid membrane, especially by the stoichiometry between PSII and PSI.
  The stoichiometry seems to be adjusted to the SPD of growth light.
  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g. @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
  The possible involvement of the change in the composition within the respective photosystems in the SPD acclimation was also suggested [@Walters_Horton1995bPlanta; @Murakami_et_al2016PP].
  <!-- Galka_et_al2012PC -->
  The adjustments in the EED properties might help the leaves to keep the high photosynthetic quantum yield under growth light.
  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
  Although a slight imbalance in the EED might be covered up by the state transitions, the long-term adjustments in the EED properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].

  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of the ETR and thereafter the *P*~n~ to the SPD of measuring light.
  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
  The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under light provided by cool-white fluorescent lamps with yellow Plexglas (FR-poor PSII-light) and incandescent bulbs with red Plexglas (FR-rich PSI-light), and subsequently measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-light.
  When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
  Similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  @Hogewoning_et_al2012PC observed the interaction in the photosynthetic quantum yield of CO~2~ uptake using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 monochromatic LED light as measuring light.
  They demonstrated that the interaction cannot occur only in the case growth light was used as measuring light but also in the case the other SPDs of light was used.
  @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and artificial sunlight (PSI-light) as measuring light.
  The potential problem in the use of BR-light for the *P*~n~ measurements was clearly demonstrated.

  These reports might suggest that the EED property of a leaf is tuned to the PSII/PSI-biased level of growth light.
  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under measuring light with the same PSII/PSI-biased level to that of growth light (Fig. 2).
  When leaves grown under different SPDs of light are compared and evaluated under a single-level SPD of light, the results should be inevitably biased depending on the SPD of measuring light.

@@

<!-- ![Fig. 2  The likely cause of the interaction of the spectral PFD distributions (SPD) of growth light and measuring light on the electron transport rate (ETR) via the excitation energy distribution (EED)](FigPath.png) -->

@@

```{r child = "~/Dropbox/Publish/ECB2016Review/Sup1.Rmd"}

>>>>

---
title: "A practical guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light conditions"
author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
bibliography: ~/GitHub/BeeLabR/BibTex/with.bib
csl: ECB.csl
header-includes:
  - \setmainfont{Helvetica Neue} 
  - \usepackage{zxjatype} # 日本語を使う
  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォント
  - \usepackage{lscape} # 図を回転する
  - \newcommand{\blandscape}{\begin{landscape}} # 図回転用のbegin command
  - \newcommand{\elandscape}{\end{landscape}} # 図回転用のend command
  - \usepackage{setspace} # 行間の調節
  - \newcommand{\bdoublespace}{\begin{spacing}{1.5}} # 行間を広げるbegin command
  - \newcommand{\edoublespace}{\end{spacing}{1.5}} # 行間を広げるbegin command

output:
  html_document:
    toc: TRUE
    depth: 3
    theme: sandstone
    self_contained: TRUE
    fig_caption: TRUE
    pandoc_args: [
    "--latexmathml"
    ]
  # word_document:
  #   pandoc_args: [
  #   "--latexmathml"
  #   ]
---

@JIS_sunlight

```{r load, echo = F, message = F}
rm(list = ls())

evalFig <- T
if(evalFig){
devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup_silent.R")
} else {
library(knitr)
}

opts_chunk$set(cache = F, echo = FALSE, fig.width = 5, fig.height = 5,
               out.width = '500pixel', out.height = '500pixel', dpi = 100,
               message = FALSE, warning = FALSE, eval = T)
```

```{r Captions, eval = evalFig}
CapETRs <-
  "Fig. 1  The conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR). Electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured using PSII-light (A, C) and PSI-light (B, D) were shown."

CapEED <-
  "Fig. 2  The excitation balance between photosystems in response to wavelength of light."

CapInteract <-
  "Fig. 3  The conceptual diagram of the photosynthetic electron transport rates per absorbed photons by the photosystems grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."

CapSPD <-
  "Fig. 4  The spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N<sup>1</sup>), metal halide lamp (MH; M220FCELS-W/BUD<sup>1</sup>), and, high-pressure sodium lamp (HPS; NH220FLS<sup>1</sup>), (b) blue (B; HBL3-3S55-LE<sup>2</sup>), red (R; SRK3-3A80-LE<sup>2</sup>), far-red (FR; L735-36AU<sup>3</sup>), and white (W; NSPW310DS<sup>4</sup>) light-emitting diodes, and (c) incident and leaf transmitted sunlight. The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown. The distribution of sunlight was adopted from JIS C 8904-3. The distribution of the leaf transmitted sunlight was calculated from that of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al. 2016). The far-red waveband (700--750 nm) is filled in grey. <br><sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan."
```

@@

```{r EED, eval = evalFig}
library(EBImage)
which_mean <- function(x) x %>% which %>% mean
Join_by <- function(x, y) join(x, y, by = "wavelength")

  Hoge_PSII <- readImage("~/Dropbox/Publish/2016PgEstimate/Data/Hoge_PSII.png")
  Hoge_PSI <- readImage("~/Dropbox/Publish/2016PgEstimate/Data/Hoge_PSI.png")

  Abs_PSII <-
    (Hoge_PSII[, , 1] < .8 & Hoge_PSII[, , 3] > .8) %>%
    .@.Data %>%
    data.frame %>%
    t %>%
    aaply(.margins = 2, .fun = which_mean) %>%
    data.frame(wavelength = seq(400, 800, by = 1), abs = (dim(Hoge_PSII)[2] - .)) %>%
    select(wavelength, PSII = abs)

  Abs_PSI <-
    (Hoge_PSI[, , 1] > .8 & Hoge_PSI[, , 3] < .8) %>%
    .@.Data %>%
    data.frame %>%
    t %>%
    aaply(.margins = 2, .fun = which_mean) %>%
    data.frame(wavelength = seq(400, 800, by = 1), abs = (dim(Hoge_PSI)[2] - .)) %>%
    select(wavelength, PSI = abs)

Mole_abs <-
  Reduce(Join_by, list(Abs_PSII, Abs_PSI)) %>%
  filter(wavelength %% 1 == 0)

Abs_ratio <-
  function(cut_row, simulate){
    simulate_dat <-
      simulate %>% slice(cut_row)

    Infos <-
      data.frame(`L_RCII` = simulate_dat$L_trimer_per_RCII,
                 `L2_L1L2` = simulate_dat$L_trimer_to_PSII,
                 `RCI_RCII` = simulate_dat$RCI_per_RCII)

    Mole_abs %>%
      transmute(
        wavelength,
        # AlltoPSII = ((PSII + Infos[1, 1] * Infos[1, 2] * LHCII) / (Infos[1, 3] * PSI + PSII + Infos[1, 1] * LHCII))
        AlltoPSII = PSII / (PSII + Infos[1,3] * PSI)
      ) %>%
      list(data = ., Info = Infos) %>%
      return
  }

EEDs <-
  Mole_abs %>%
  transmute(
    wavelength,
    AlltoPSII = PSII / (1.5 * PSI + PSII)
  ) %>%
  filter(AlltoPSII >= 0)  %>%
  replace_na(list(AlltoPSII = 0)) %>%
  ggplot(aes(x = wavelength, y = AlltoPSII)) +
  theme_bw2() +
  gg_xy(c(380, 770, -0.05, 1.05)) +
  # geom_ribbon(aes(ymin = AlltoPSII_max, ymax = AlltoPSII_min), col = "grey50") +
  geom_line() +
  xlab("Wavelength [nm]") + ylab("")
```

```{r Spectra, eval = evalFig}

# set integrate ranges
PFD_integrate_min <- 350
PFD_integrate_max <- 750

IntegratePFD <- 100

panel_names <- c("(a)", "(b)", "(c)")

# HID_raw <-
#   fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)
# 
# HIDs <-
#   HID_raw %>%
#   setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
#   select(1, HPS_ = 12, MH_ = 21)
FL_Ocean_raw <-
  fread("~/Dropbox/materials/SPD_FL.csv") %>%
  transmute(wavelength = `Wavelength[nm]`, value = FL) %>%
  na.omit

FL_Ocean_PFD <-
  smooth.spline(FL_Ocean_raw$wavelength, FL_Ocean_raw$value) %>%
    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
    .$y %>%
  sum

FL_Ocean <-
  FL_Ocean_raw %>%
  mutate(value = value * 100 / FL_Ocean_PFD, variable = "FL")

HPS_Ocean_raw <-
  fread("~/Dropbox/materials/SPD_HPS.txt", skip = 50, nrow = 2000) %>%
  rename(wavelength = V1, value = V2)

HPS_Ocean_PFD <-
  smooth.spline(HPS_Ocean_raw$wavelength, HPS_Ocean_raw$value) %>%
    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
    .$y %>%
  sum

HPS_Ocean <-
  HPS_Ocean_raw %>%
  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "HPS")

MH_Ocean_raw <-
  fread("~/Dropbox/materials/SPD_MH.txt", skip = 50, nrow = 2000) %>%
  rename(wavelength = V1, value = V2)

MH_Ocean_PFD <-
  smooth.spline(MH_Ocean_raw$wavelength, MH_Ocean_raw$value) %>%
    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
    .$y %>%
  sum

MH_Ocean <-
  MH_Ocean_raw %>%
  mutate(value = value * 100 / MH_Ocean_PFD, variable = "MH")

OceanSPDs <-
  bind_rows(FL_Ocean, HPS_Ocean, MH_Ocean) %>%
  mutate(panel = panel_names[1])

Absorptances <-
  fread("~/Dropbox/materials/SpectrumCucumber.csv") %>%
  filter(Trtm %in% c("W", "WFR", "FL")) %>%
  mutate(wavelength = as.numeric(wavelength)) %>%
  filter(variable == "absorption", Trtm == "W")

Sun <-
  fread("~/Dropbox/materials/Sunlight_JIS.csv") %>%
  setnames(c("wavelength", "Sunlight")) %>%
  left_join(., Absorptances, by = "wavelength") %>%
  transmute(wavelength, Sun = Sunlight, Shade = Sunlight * (100 - ave), Absorptance = ave)

# Sun: JIS C8904-3

LEDs <-
  fread("~/Dropbox/materials/SPD_FL.csv") %>%
  transmute(wavelength = `Wavelength[nm]`, W, FR, B = B_HL, R = R_SR) %>%
  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
  gather(variable, value, -wavelength) %>%
  mutate(panel = panel_names[2]) %>%
  na.omit

SPD_labels <-
  data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 700),
             value = c(2.2, .6, 3, 4, 4.2, 3.8, 1.3, 0.6, 2),
             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sunlight", "Leaf transmitted sunlight"),
             panel = rep(panel_names,  c(3, 4, 2)))

SPD_panel <-
  data_frame(variable = "FL",
           wavelength = 400, value = 4,
           label = letters[1:3],
           panel = rep(panel_names))

SPDs <-
  Sun %>%
  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
  select(-Absorptance) %>%
  gather(variable, value, -wavelength) %>%
  mutate(panel = panel_names[3]) %>%
  bind_rows(., OceanSPDs, LEDs) %>%
  filter(between(wavelength, 380, 820)) %>%
  ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
  theme_bw2() +
  theme(strip.background = element_blank(),
        strip.text = element_blank(),
        panel.grid.major = element_blank()) +
  geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey90", col = NA) +
  geom_line() +
  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label)) +
  geom_text(data = SPD_panel, col = "black", aes(label = panel)) +
  scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
  scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey25", "black", "black")) +
  facet_grid(panel ~ .) +
  gg_xy(c(380, 820, 0, 4.5)) +
  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))

@@

Check terms:
level

@@

  The photosynthetic rate is one of the most important and fundamental *traits of the plant (aspects? for growth? of plants*.
  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions.
  The measured rates are also used for the calculation of the other photosynthesis-related indices, such as light-, water-, and nitrogen-use efficiencies for photosynthesis.
  In agricultural and horticultural studies, the effectiveness of treatments is sometimes discussed based on the measured photosynthetic rates and calculated parameters. 
  Therefore, accurate measurements of the photosynthetic rates must be essential.

  A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for the measurement (i.e. measuring light or actinic light) affected leaf net photosynthetic rates (*P*~n~) [e.g. @McCree1972AM; @Inada1976PCP].
  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a common SPD of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies.
  One of the most widely-used measuring light is mixture of blue and red light provided by LED light sources (BR-light) installed in commercial photosynthesis analyzing systems (e.g. LI6400 and LI6400XT, LI-COR Inc.; GFS-3000, Heinz Walz GmbH).
  The use of artificial light sources enables precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf and therefore ensure the reproducibility and reliability of the experiments.

  @Walters2005JXB pointed out that measuring photosynthetic rates with a SPD of light different from that of growth light do not necessarily reflect the functioning of photosynthesis under growth conditions.
  Our recent study, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently *P*~n~ of the leaves were compared under BR-light and light with the SPD resembling that of sunlight (‘artificial’ sunlight).
  The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable under the artificial sunlight [@Murakami_et_al2016PP].
  Based on the results obtained from the measurement under BR-light, the prospective **growth (leaf photosynthetic)** rate of WFR-plants may be evaluated to be smaller than that of W-plants despite the comparable rates under sunlight.

  The effect of the SPD of growth light on *P*~n~ depends on the SPD of measuring light.
  In other words, the SPDs of growth light and measuring light interact on *P*~n~ of a leaf.
  In this short article, we introduce a plausible cause of the interaction and several articles reporting the interaction.
  We then suggest situations in which the interaction should be **particularly?** cared.
  We also discuss the good practice for selecting of the SPD of measuring light for *P*~n~ measurements.
  The SPD of light affects photosynthesis through **the other mechanisms (何のほかか、が不明瞭。EEDを上で簡単に書いておきたい)**, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP].
  Although these subjects are not referred in this article, the cited articles are available for these topics.

# How the interaction is generated? **(見出し軽すぎ)**

  Fundamental knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
  Light energy absorbed by a leaf drives the phtoosynthetic electron transport, O~2~ evolution, and CO~2~ uptake.
  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
  The reactions are powered by excitation energy derived from absorbed photons.
  The excitation energy transferred to the reaction centers of the photosystems is consumed by the photochemical reactions **in units of moles**.
  The serial photochemical reactions at PSII and PSI enables electron transfer from water to NADP^+^ (called the Z scheme).
  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membranes should be limited by the slowest step (Fig. 1).
  When the excitation energy is in excess at PSII, the **energy distribution (この書き方は，いきなりだと知らない人にはわかりにくいものと思われる。)** to PSI limits the ETR and thus the photochemical quantum yield of PSII should be lowered (Fig. 1C).
  When PSI absorbs the excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 1B).
  In both cases, the excess energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
  **Imbalanced excitation between the photosystems can harm leaves (これは強く言える？微妙)** by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
  Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.
  <!-- **おまけ部分** -->
  <!-- Note that the balanced distribution might not be a fifty-fifty. -->
  <!-- Even in a dark adapted helthy leaf, the yield of PSII cannot exceed 0.84 (i.e. Chl fluorescence parameter *F*~v~/*F*~m~). -->
  <!-- Although there is no clear consensus, the maximum yield of PSI seems to be greater than that of PSII. -->
  <!-- Therefore, under the fifty-fifty distribution, the energy supply to PSII is insufficient and that to PSI is excessive. -->
  <!-- A little bit greater distribution to PSII might be required to make maximum use of the absorbed photons. -->
  <!-- Gentyに触れるか？AEF -->

  <!-- The imbalance in the EED between the photosystems is supposed to occur ordinarily (どこで？太陽光？). -->
  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*. **(図があるとわかりやすい)**
  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  This is because only chl *a* can absorb the longer wavelengths of light and PSI contains a greater amount of chl *a* than PSII.
  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependencies of the excitation is a determinant of the EED under a given SPD of light.
  In studies on the acclimation of the photosynthetic apparatus to the SPD of growth light, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g. @Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Fan_et_al2007BBA; @Pfannschmidt_et_al2009AB; @Hogewoning_et_al2012PC].
  **This categorization is defined in the relative scale, not in the absolute scale.「absolute」と「relative」が何を指しているのかなど，，もう少し具体的に書きたい。ある特定の葉に対してのみ定義できる**
  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 1A), can overexcite PSII in PSI-light-grown leaves (Fig. 1C).
  Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.

  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid components, especially by the stoichiometry between PSII and PSI.
  The stoichiometry seems to be adjusted to the SPD of growth light.
  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g. @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
  **Possible involvement of the change in the composition within the respective photosystems in the acclimation to SPD was also suggested [@Walters_Horton1995bPlanta; @Murakami_et_al2016PP]. 具体的に何か、言っとくべき**
  <!-- Galka_et_al2012PC -->
  The adjustments in the EED properties might help the leaves to keep the high photosynthetic quantum yield under growth light.
  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
  Although a slight imbalance in the EED might be compensated for by the state transitions, the long-term adjustments in the EED properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].

  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of ETR and thereby *P*~n~ to the SPD of measuring light.
  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
  The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  In their pioneering study, @Chow_et_al1990PNAS grew *Pisum sativum* plants under light provided by cool-white fluorescent lamps with yellow Plexiglas (PSII-light) and incandescent bulbs with red Plexiglas (PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by the leaf---under the PSII- and PSI-light reciprocally.
  When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
  Similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  @Hogewoning_et_al2012PC observed the interaction in the photosynthetic quantum yield of CO~2~ uptake using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 kinds of monochromatic LED light as measuring light.
  **They demonstrated that the interaction cannot occur only in the case growth light was used as measuring light but also in the case the other SPDs of light was used.**
  @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and the artificial sunlight (PSI-light) as measuring light.
  It was clearly demonstrated that the use of BR-light for *P*~n~ measurements could result in the biased evaluation.

  These reports suggest that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of growth light.
  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under measuring light with a PSII/PSI-biased level similar to that of growth light (Fig. 2).
  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of light, the results should be inevitably biased depending on the SPD of measuring light.

@@

```{r, eval = evalFig, fig.cap = CapEED}
EEDs
```

@@

```{r FigSPD, eval = evalFig, fig.width = 5, fig.height = 5, out.width = '500pixel', out.height = '500pixel'}
SPDs
```
